Simulation of Nano Particles in a Laser Trap

### 2017-02-10 doc/draft2.tex
updates

>>>>

To see the comparison between the different temperatures of the impinging gas temperatures, three values for the pressure are chosen: $P=0.1$, $P=0.5$
and $P=1.0$. The simulation results for the center of mass temperature, the internal temperature and the temperature of the outgoing gas particles are
plotted for each of the pressure values and both temperatures.
